Data Exploration

### 2019-02-21 src/data_exploration.Rmd
stack building - could do with loop

```{r}
library(dismo)
library(rJava)
jar <- paste(system.file(package="dismo"), "C:/Users/bunny/Documents/GitHub/Chapter_1/packrat/lib/x86_64-w64-mingw32/3.5.1/dismo/java/maxent.jar", sep='')
p
testmax <- maxent(janpresmax, janabmax)
```

>>>>

zt stratified stack with layer names that match swd
```{r}
chl_surface <- raster(list.files("../data/jan_test_86.9", pattern = glob2rx("*1998_01*chl_surface_86.9294*.asc"), full.names = TRUE))
names(chl_surface) <- "chl_surface"
nao_sample <- raster(list.files("../data/jan_test_86.9", pattern = glob2rx("*1998_01*nao_sample_86.9294*.asc"), full.names = TRUE))
names(nao_sample) <- "nao_sample"
nao_winter <- raster(list.files("../data/jan_test_86.9", pattern = glob2rx("*1998_01*nao_winter_86.9294*.asc"), full.names = TRUE))
names(nao_winter) <- "nao_winter"
o2_depth <- raster(list.files("../data/jan_test_86.9", pattern = glob2rx("*1998_01*o2_depth_86.9294*.asc"), full.names = TRUE)) 
names(o2_depth) <- "o2_depth"
salinity_depth <- raster(list.files("../data/jan_test_86.9", pattern = glob2rx("*1998_01*salinity_depth_86.9294*.asc"), full.names = TRUE))
names(salinity_depth) <- "salinity_depth"
temp_depth <- raster(list.files("../data/jan_test_86.9", pattern = glob2rx("*1998_01*temp_depth_86.9294*.asc"), full.names = TRUE))
names(temp_depth) <- "temp_depth"

stack1998_01_86.9294 <- stack(chl_surface, nao_sample, nao_winter, o2_depth, salinity_depth, temp_depth)

asclist <- stack(list.files("../data/jan_test_86.9", pattern = glob2rx("*1998_01*_86.9294*.asc"), full.names = TRUE))    # this folder currently contains other dummy files. its just a test to automate stacks
ascfile <- names(asclist[[1]])
ascyear <- as.character(sapply(strsplit(ascfile[[1]], "_"), "[[", 1))
ascmonth <- as.character(sapply(strsplit(ascfile[[1]], "_"), "[[", 2))
ascdepth <- as.character(sapply(strsplit(ascfile[[1]], "_"), "[[", 5))
ascname <- paste(ascyear, ascmonth, ascdepth, sep = "_") #once you figure out how to rename the layers in the stack, you will rename the stack this () or not - maybe just manual
asclist # now need to rename to match maxent expectations

```{r}
library(dismo)
library(rJava)
jar <- paste(system.file(package="dismo"), "C:/Users/bunny/Documents/GitHub/Chapter_1/packrat/lib/x86_64-w64-mingw32/3.5.1/dismo/java/maxent.jar", sep='')
file.exists(jar)
testmax <- maxent(janpresabmax, janpresabmax$occurrence)
